### 2019-08-05 reports/thesis/book.tex
Front cover
compound poisson
Corrections in 3 and 4

\newcommand{\RSS}{\mathrm{RSS}}
\newcommand{\euler}{\mathrm{e}}
\newcommand{\diff}{\mathrm{d}}
\newcommand{\T}{^\textup{T}}
\newcommand{\dotdotdot}{_{\phantom{.}\cdots}}
\newcommand{\BIC}{\mathrm{BIC}}
\newcommand{\AIC}{\mathrm{AIC}}

@@

\begin{titlingpage}
\centering
{\LARGE Characterisation of Computed Tomography Noise in Projection Space with Applications in Additive Manufacturing \par}
\vspace{1cm}
{\Large Sherman E.~Lo\par}
{\Large Doctor of Philosophy in Statistics\par}
\vfill
{\Large University of Warwick\par}
{\Large Department of Statistics\par}
{\Large September 2019\par}
\end{titlingpage}

@@

This work is funded by the EPSRC and MRC Centre for Doctoral Training in Next Generation Statistical Science: The Oxford-Warwick Statistics Programme (EP/L016710/1). I would like to thank my cohort for the friendship and collaboration during the programme: Nathan Cunningham, Giuseppe di Benedetto, Beniamino Hadj-Amar, Jack Jewson, Ella Kaye, Leon Law, Kaspar Martens, Marcin Mider, Xenia Miscouridou, Paul Vanetti and Andi Wang.

>>>>

\newcommand{\RSS}{\mathrm{RSS}}
\newcommand{\euler}{\mathrm{e}}
\newcommand{\diff}{\mathrm{d}}
\newcommand{\T}{^\textup{T}}
\newcommand{\dotdotdot}{\cdots}
\newcommand{\BIC}{\mathrm{BIC}}
\newcommand{\AIC}{\mathrm{AIC}}

@@

\begin{titlingpage}
\centering
{\LARGE Characterisation of Computed Tomography Noise in Projection Space with Applications to Additive Manufacturing \par}
\vspace{1cm}
{\Large Sherman E.~Lo\par}
{\Large Doctor of Philosophy in Statistics\par}
\vfill
\includegraphics[width = 0.75\textwidth]{../figures/frontCover.jpg}
\vfill
{\Large University of Warwick\par}
{\Large Department of Statistics\par}
{\Large September 2019\par}
\end{titlingpage}

@@

This work is funded by the EPSRC and MRC Centre for Doctoral Training in Next Generation Statistical Science: The Oxford-Warwick Statistics Programme (EP/L016710/1). I would like to thank my cohort for the friendship and collaboration during the programme: Nathan Cunningham, Giuseppe di Benedetto, Beniamino Hadj-Amar, Jack Jewson, Ella Kaye, Leon Law, Kaspar M\"{a}rtens, Marcin Mider, Xenia Miscouridou, Paul Vanetti and Andi Wang.

### 2019-08-05 reports/thesis/chapters/3_compoundPoisson.tex
Corrections in 3 and 4

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\mainSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonlambda1alpha1beta1.eps}
        \caption{Left: Observed and expected frequency of a zero. Right: Histogram and p.d.f.~of non-zero values.}
    \end{subfigure}
    }
    \vspace{2em}
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonlambda1alpha1beta1.eps}
        \caption{Q-Q plot}
    \end{subfigure}
    }
    \caption{1\,000 $\CPoisson(1,1,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.~evaluated using the exact method. In a), the dotted red line shows the $\Phi(\pm1)$ quantile of the expected frequency or frequency density.}
    \label{fig:compoundPoisson_histogram_1_1_1}
\end{figure}

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\mainSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonlambda1alpha100beta1.eps}
        \caption{Left: Observed and expected frequency of a zero. Right: Histogram and p.d.f.~of non-zero values.}
    \end{subfigure}
    }
    \vspace{2em}
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonlambda1alpha100beta1.eps}
        \caption{Q-Q plot}
    \end{subfigure}
    }
    \caption{1\,000 $\CPoisson(1,100,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.~evaluated using the exact method. In a), the dotted red line shows the $\Phi(\pm1)$ quantile of the expected frequency or frequency density.}
    \label{fig:compoundPoisson_histogram_1_100_1}
\end{figure}

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda1alpha1beta1.eps}
        \caption{$\CPoisson(1,1,1)$ Normal approx.}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda1alpha1beta1.eps}
        \caption{$\CPoisson(1,1,1)$ saddlepoint approx.}
    \end{subfigure}
    }
    \vspace{1em}
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda1alpha100beta1.eps}
        \caption{$\CPoisson(1,100,1)$ Normal approx.}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda1alpha100beta1.eps}
        \caption{$\CPoisson(1,100,1)$ saddlepoint approx.}
        \label{fig:compoundPoisson_histogram_approx_1_100_1}
    \end{subfigure}
    }
    \caption{1\,000 $\CPoisson(1,\alpha,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.~evaluated using approximate methods. The dotted red line shows the $\Phi(\pm1)$ quantile of the expected frequency density.}
    \label{fig:compoundPoisson_histogram_approx}
\end{figure}

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonlambda10alpha1beta1.eps}
        \caption{Histogram - Exact method}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonlambda10alpha1beta1.eps}
        \caption{Q-Q plot - Exact method}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda10alpha1beta1.eps}
        \caption{Histogram - Normal approx.}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonNormlambda10alpha1beta1.eps}
        \caption{Q-Q plot - Normal approx.}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda10alpha1beta1.eps}
        \caption{Histogram - Saddlepoint approx.}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonSaddlelambda10alpha1beta1.eps}
        \caption{Q-Q plot - Saddlepoint approx.}
    \end{subfigure}
    }
    \caption{1\,000 $\CPoisson(10,1,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f. On the left, the dotted red line shows the $\Phi(\pm1)$ quantile of the expected frequency density.}
    \label{fig:compoundPoisson_histogram_10_1_1}
\end{figure}

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonlambda100alpha100beta1.eps}
        \caption{Histogram - Exact method}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonlambda100alpha100beta1.eps}
        \caption{Q-Q plot - Exact method}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda100alpha100beta1.eps}
        \caption{Histogram - Normal approx.}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonNormlambda100alpha100beta1.eps}
        \caption{Q-Q plot - Normal approx.}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda100alpha100beta1.eps}
        \caption{Histogram - Saddlepoint approx.}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonSaddlelambda100alpha100beta1.eps}
        \caption{Q-Q plot - Saddlepoint approx.}
    \end{subfigure}
    }
    \caption{1\,000 $\CPoisson(100,100,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f. On the left, the dotted red line shows the $\Phi(\pm1)$ quantile of the expected frequency density.}
    \label{fig:compoundPoisson_histogram_100_1_1}
\end{figure}

>>>>

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\mainSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonlambda1alpha1beta1.eps}
        \caption{Left: Observed and expected frequency of a zero. Right: Histogram and p.d.f.~of non-zero values.}
    \end{subfigure}
    }
    \vspace{2em}
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonlambda1alpha1beta1.eps}
        \caption{Q-Q plot}
    \end{subfigure}
    }
    \caption{1\,000 $\CPoisson(1,1,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.~evaluated using the exact method. In a), the dotted red line shows the $\Phi(+1)-\Phi(-1)$ confidence interval of the expected frequency or frequency density.}
    \label{fig:compoundPoisson_histogram_1_1_1}
\end{figure}

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\mainSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonlambda1alpha100beta1.eps}
        \caption{Left: Observed and expected frequency of a zero. Right: Histogram and p.d.f.~of non-zero values.}
    \end{subfigure}
    }
    \vspace{2em}
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonlambda1alpha100beta1.eps}
        \caption{Q-Q plot}
    \end{subfigure}
    }
    \caption{1\,000 $\CPoisson(1,100,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.~evaluated using the exact method. In a), the dotted red line shows the $\Phi(+1)-\Phi(-1)$ confidence interval of the expected frequency or frequency density.}
    \label{fig:compoundPoisson_histogram_1_100_1}
\end{figure}

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda1alpha1beta1.eps}
        \caption{$\CPoisson(1,1,1)$ Normal approx.}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda1alpha1beta1.eps}
        \caption{$\CPoisson(1,1,1)$ saddlepoint approx.}
    \end{subfigure}
    }
    \vspace{1em}
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda1alpha100beta1.eps}
        \caption{$\CPoisson(1,100,1)$ Normal approx.}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda1alpha100beta1.eps}
        \caption{$\CPoisson(1,100,1)$ saddlepoint approx.}
        \label{fig:compoundPoisson_histogram_approx_1_100_1}
    \end{subfigure}
    }
    \caption{1\,000 $\CPoisson(1,\alpha,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.~evaluated using approximate methods. The dotted red line shows the $\Phi(+1)-\Phi(-1)$ confidence interval of the expected frequency density.}
    \label{fig:compoundPoisson_histogram_approx}
\end{figure}

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonlambda10alpha1beta1.eps}
        \caption{Histogram - Exact method}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonlambda10alpha1beta1.eps}
        \caption{Q-Q plot - Exact method}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda10alpha1beta1.eps}
        \caption{Histogram - Normal approx.}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonNormlambda10alpha1beta1.eps}
        \caption{Q-Q plot - Normal approx.}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda10alpha1beta1.eps}
        \caption{Histogram - Saddlepoint approx.}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonSaddlelambda10alpha1beta1.eps}
        \caption{Q-Q plot - Saddlepoint approx.}
    \end{subfigure}
    }
    \caption{1\,000 $\CPoisson(10,1,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f. On the left, the dotted red line shows the $\Phi(+1)-\Phi(-1)$ confidence interval of the expected frequency density.}
    \label{fig:compoundPoisson_histogram_10_1_1}
\end{figure}

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonlambda100alpha100beta1.eps}
        \caption{Histogram - Exact method}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonlambda100alpha100beta1.eps}
        \caption{Q-Q plot - Exact method}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda100alpha100beta1.eps}
        \caption{Histogram - Normal approx.}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonNormlambda100alpha100beta1.eps}
        \caption{Q-Q plot - Normal approx.}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda100alpha100beta1.eps}
        \caption{Histogram - Saddlepoint approx.}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonSaddlelambda100alpha100beta1.eps}
        \caption{Q-Q plot - Saddlepoint approx.}
    \end{subfigure}
    }
    \caption{1\,000 $\CPoisson(100,100,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f. On the left, the dotted red line shows the $\Phi(+1)-\Phi(-1)$ confidence interval of the expected frequency density.}
    \label{fig:compoundPoisson_histogram_100_1_1}
\end{figure}
